The Right Way to Search Evolving Graphs

### 2016-03-04 paper.tex
update new timing figure

We generate a group of random (directed) \texttt{IntEvolvingGraph}s
with $1.0\times 10^5$ active nodes and $10$ time stamps.
The first random \texttt{IntEvolvingGraph} in the group has 
$1.0 \times 10^8$ static edges.
We consecutively add $5.0\times 10^7$
random static edges to this \texttt{IntEvolvingGraph}. For example, 
the second random \texttt{IntEvolvingGraph} in the group has about $1.5 \times 10^8$ static edges and the third
has about $2.0 \times 10^8$ static edges.
% At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
% probability $p$. 
Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. However, the
causal edge set $E'$ can grow at most by $O(\tilde E)$, so it suffices to demonstrate
linear scaling in $|\tilde E|$. 
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a Linux system with Intel(R) Xeon(R) CPU E7-8850 @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.
By doing this experiment, we find that it takes longer and longer time to 
add new static edges, since we also need to include
all the causal edges introduced by these new static edges.

>>>>

We generate a sequence of random (directed) \texttt{IntEvolvingGraph}s
with $1.0\times 10^5$ active nodes and $10$ time stamps.
The first \texttt{IntEvolvingGraph} in the sequence has about
$1.0 \times 10^8$ static edges.
We consecutively add new
random static edges to this \texttt{IntEvolvingGraph}. For example, 
the second random \texttt{IntEvolvingGraph} in the sequence 
has about $1.5 \times 10^8$ static edges and the third
has $1.8 \times 10^8$ static edges.
% At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
% probability $p$. 
Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. However, the
causal edge set $E'$ can grow at most by $O(\tilde E)$, so it suffices to demonstrate
linear scaling in $|\tilde E|$. 
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a Linux system with Intel(R) Xeon(R) CPU E7-8850 @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.
